---
title: "Bug hunt"
author: "Leonie"
date: "2024-07-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Stuart - Item selection
## Sample split
```{r}
library(stuart)
#, 0.4525
split <- holdout(df4, prop = 0.5475, grouping = NULL, seed = 2024, determined = NULL)
lapply(split, nrow) #check size of sample

# Accessing the split datasets
df_train <- split$calibrate
df_test <- split$validate

# Remove the 'determined' column by setting it to NULL
df_train$determined <- NULL
df_test$determined <- NULL

# adding the partially completed ones to the df train
df_train <- rbind(df_train, df_partial)

# exclude everything exept the dl items
df_train <- df_train[,3:71]

df_test_dl <- df_test[,3:71]
```

## using mice 
```{r, echo=FALSE}
imputed_training_data <- mice(df_train, m=5, method='pmm', maxit=50)
imputed_training_data_c <- complete(imputed_training_data, 1)

imputed_test_data <- mice(df_test_dl, m=5, method='pmm', maxit=50)
imputed_test_data_c <- complete(imputed_test_data, 1)
```

```{r}
write.csv2(imputed_training_data_c, "imputed_training_data_c.csv")
write.csv2(df_train, "df_train.csv")
```

```{r}

fs<-list(Comprehension=c('F1F1','F1F2','F1F3','F1F4','F1F5','F1F6','F1F7','F1F8',
                           'F1F9','F1F10','F1F11','F1F12','F1F13','F1F14'),
           Evaluation=c('F2F1','F2F2','F2F3','F2F4','F2F5','F2F6','F2F7','F2F8',
                        'F2F9','F2F10','F2F11','F2F12','F2F13','F2F14','F2F15',
                        'F2F16','F2F17','F2F18','F2F19','F2F20'),
           Integration=c('F3F1','F3F2','F3F3','F3F4','F3F5','F3F6','F3F7','F3F8','F3F9'),
           Communication=c('F4F1','F4F2','F4F3','F4F4','F4F5','F4F6','F4F7','F4F8'),
           Statistics=c('F5F1','F5F2','F5F3','F5F4','F5F5','F5F6','F5F7','F5F8',
                        'F5F9','F5F10','F5F11','F5F12','F5F13','F5F14','F5F15',
                        'F5F16','F5F17','F5F18')
                           )
```

## ordinal data transformation?
```{r}
ords <- imputed_training_data_c[, names(imputed_training_data_c)%in%unlist(fs)]
ords <- lapply(ords, as.ordered)
ords <- do.call(data.frame, ords)
```

## Objective-Function
```{r}
library(stuart)

# Define the theoretical nu matrix 
theoretical_nu <- matrix(c(5, 4, 2, 1,  # Factor 1 items
                      5, 4, 2, 1,  # Factor 2 items
                      5, 4, 2, 1,  # Factor 3 items
                      5, 4, 2, 1,  # Factor 4 items
                      5, 4, 2, 1), # Factor 5 items
                    nrow = 4, byrow = TRUE,
                    dimnames = list(c("Item1", "Item2", "Item3", "Item4"),
                                    c("Factor1", "Factor2", "Factor3", "Factor4", "Factor5")))

# Convert the matrix to a vector
nu_vector <- c(theoretical_nu)

# Calculate the standard deviation of the vector
ideal_sd <- sd(nu_vector)

# Print the ideal standard deviation
print(ideal_sd) #1.62

# Use 'ideal_sd' in my objective function
#ordinal data
obj <- function(chisq, df, pvalue,rmsea.scaled, srmr, cfi.scaled, crel, nu) {
  out1 = 0.5-(0.5/(1 + exp(- 100 * (rmsea.scaled-.05))))
  out2 = 0.5-(0.5/(1 + exp(- 100 * (srmr-.05))))
  out3 = (1/(1 + exp(- 100 * (cfi.scaled-.95))))
  #out4 = -(sd(nu) - 1.62)^2 + 1.62^2 # Quadratic function peaking at 'ideal_sd'
  out = (out1 + out2 + out3 )/3 #+ out4)/4
  return(out)                                
}

#stuart:::objective.preset
obj_default <- function(chisq, df, pvalue, rmsea, srmr, crel) {
                      1/(1 + exp(-10 * (crel - 0.6))) + 0.5 * (1 - (1/(1 + exp(-100 * 
                     (rmsea - 0.05))))) + 0.5 * (1 - (1/(1 + exp(-100 * (srmr - 
                      0.06)))))
                       }
#stuart:::objective.preset2
obj_default2 <- function(chisq, df, pvalue, rmsea, srmr, crel, nu) {
                      1/(1 + exp(-10 * (crel - 0.6))) + 0.5 * (1 - (1/(1 + exp(-100 * 
                     (rmsea - 0.05))))) + 0.5 * (1 - (1/(1 + exp(-100 * (srmr - 
                      0.06))))) - (sd(nu) - 1.62)^2 + 1.62^2 + 1e-6
                       }

```


```{r}
combinations(imputed_training_data_c, fs,4)
```
## Genetic Algorithm
### Kfold-Crossvalidation
```{r}

############ k-Folding #########################

# erster der holdout wird an kfold weitergegeben

# Call the kfold function with factor.structure as an argument
kfold_sel <- kfold(
  'gene', 
  k = 3, 
  data = imputed_training_data_c, 
  factor.structure = fs,  # Pass the variable directly
  max.invariance = "strict", 
  capacity = list(4, 4, 4, 4, 4), 
  seed = 2024,
  seeded.search = TRUE,
  auxiliary = NULL,
  software = "lavaan",
  cores = 4,
  objective = obj_default,
  ignore.errors = TRUE,
  burnin = 5,
  generations = 300,
  individuals = 64,
  selection = "tournament",
  selection.pressure = NULL,
  elitism = NULL,
  reproduction = 0.5,
  mutation = 0.05,
  mating.index = 0,
  mating.size = 0.25,
  mating.criterion = "similarity",
  immigration = 0,
  convergence.criterion = "geno.between",
  tolerance = NULL,
  reinit.n = 1,
  reinit.criterion = "geno.between",
  reinit.tolerance = NULL,
  reinit.prop = 0.75,
  schedule = "run",
  analysis.options = NULL,
  suppress.model = FALSE,
  remove.details = TRUE
)
#########################################################
summary(kfold_sel)

inspect(kfold_sel$final, 'est')
inspect(kfold_sel$final, 'fit')

lavaan::summary(kfold_sel$final, standardized = TRUE) 
#lavaan::inspect(selection$final, 'est')$nu
```
- First Time it worked:
SUMMARY OF ANALYSIS:

Number of Folds: 3 
Analysis Type: gene 
Estimation Software: lavaan 
Models Estimated: 61760 
Time Required: 1175.532 seconds

Crossvalidation Results with STRICT Invariance:

Average Jaccard Similarity: Comprehension: 0.422, Evaluation: 0.295, Integration: 0.295, Communication: 0.600, Statistics: 0.359

Constructed Subtests: (k = 1)
Comprehension: F1F2 F1F6 F1F8 F1F10
Evaluation: F2F2 F2F4 F2F14 F2F15
Integration: F3F3 F3F4 F3F5 F3F9
Communication: F4F1 F4F3 F4F6 F4F7
Statistics: F5F3 F5F4 F5F15 F5F18

```{r}
# Call the kfold function with factor.structure as an argument
kfold_sel2 <- kfold(
  'gene', 
  k = 3, 
  data = imputed_training_data_c, 
  factor.structure = fs,  # Pass the variable directly
  max.invariance = "strict", 
  capacity = list(4, 4, 4, 4, 4), 
  seed = 2024,
  seeded.search = TRUE,
  auxiliary = NULL,
  software = "lavaan",
  cores = 4,
  objective = obj_default2,
  ignore.errors = TRUE,
  burnin = 5,
  generations = 500,
  individuals =100,
  selection = "tournament",
  selection.pressure = NULL,
  elitism = NULL,
  reproduction = 0.5,
  mutation = 0.05,
  mating.index = 0,
  mating.size = 0.25,
  mating.criterion = "similarity",
  immigration = 0,
  convergence.criterion = "geno.between",
  tolerance = NULL,
  reinit.n = 1,
  reinit.criterion = "geno.between",
  reinit.tolerance = NULL,
  reinit.prop = 0.75,
  schedule = "run",
  analysis.options = NULL,
  suppress.model = FALSE,
  remove.details = TRUE
)
#########################################################
summary(kfold_sel2)

inspect(kfold_sel2$final, 'est')
inspect(kfold_sel2$final, 'fit')

lavaan::summary(kfold_sel2$final, standardized = TRUE) 
lavaan::inspect(kfold_sel2$final, 'est')$nu
```