---
title: "Analysis"
author: "Leonie"
date: "2024-04-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# to clear environment while working
rm(list=ls()) 

usethis::use_git_config(
  user.name = "LeonieHagitte",
  user.email = "leonie.hagitte@student.hu-berlin.de",
  init.defaultBranch = "devl")

```

```{r}
if(!requireNamespace("remotes"))
install.packages("remotes")
remotes::install_github("aaronpeikert/repro")
repro::automate() #creating a Dockerfile.    ####################### BUG ######
repro::use_docker()
repro::use_gha_docker() #GitHub action (GHA) is a cloud service that runs software when certain events trigger it.Add a GitHub Action to build the required Docker image with

# Install or update 'renv' package from CRAN if needed
# Load 'renv' package
library(renv)

# Initialize 'renv' in your project
renv::init()

# Activate the project-specific 'renv' environment
renv::activate()

# Install required packages for your project
#renv::install()

# Update renv.lock file
renv::snapshot()

```

```{r}
install.packages('semPower')
library(semPower)
```

# Poweranalyse mit SemPower ohne Model
```{r}
ap <- semPower.aPriori(effect = .05, effect.measure = 'RMSEA', 
                       alpha = .05, power = .80, df = 150)
summary(ap)
```

# Poweranalyse mit SemPower mit Model
```{r}
powerLI <- semPower.powerLI(
  type = 'a-priori', alpha = .05, power = .80,
  comparison = 'configural',
  nullEffect = 'metric',
  nIndicator = c(4, 4, 4, 4, 4),
  loadM = c(.6, .7, .6, .7, .7),
  autocorResiduals = TRUE
)
# show summary
summary(powerLI)

```
## Results Printed
semPower: A priori power analysis

 Simulated power based on 500 successful replications.
 Note that simulated a-priori power analyses are only approximate,
 unless the number of replications is large.
                                               
                           Analytical Simulated
                                               
 F0                        0.029922   0.030359 
 RMSEA                     0.043245   0.043560 
 Mc                        0.985150   0.984935 
                                               
 df                        16         16       
 Required Num Observations 645        613      
                                               
 Critical Chi-Square       26.29622   26.29622 
 NCP                       19.26999   18.57971 
 Alpha                     0.050000   0.050000 
 Beta                      0.199943   0.212000 
 Power (1 - Beta)          0.800057   0.788000 
 Implied Alpha/Beta Ratio  0.250072   0.235849 


 Simulation Results:
                                                     
 Convergence Rate (%) of the H0 model        100.00  
                                                     
 Chi-Square Bias (%)                                 
 H0 Model                                    0.68    
 H1 Model                                    1.48    
 H0-H1 Difference                            -2.03   
                                                     
 Chi-Square KS-Distance                              
 H0 Model                                    0.017362
 H1 Model                                    0.027111
 H0-H1 Difference                            0.014788
                                                     
 Rejection Rate (%)                                  
 H0 Model                                    32.80   
 H1 Model                                    8.60    
                                                     
 Average Parameter Bias (%) in the H1 Model:         
 Loadings                                    0.06    
 Variances/Covariances                       0.00    

```{r}
model <- "
# Measurement model
y1 =~ x1 + x2 + x3 + x4
y2 =~ x5 + x6 + x7 + x8
y3 =~ x9 + x10 + x11 + x12
y4 =~ x13 + x14 + x15 + x16
y5 =~ x17 + x18 + x19 + x20

# Factor variances
y1 ~~ y1
y2 ~~ y2
y3 ~~ y3
y4 ~~ y4
y5 ~~ y5

# Factor correlations
y1 ~~ y2
y1 ~~ y3
y1 ~~ y4
y1 ~~ y5
y2 ~~ y3
y2 ~~ y4
y2 ~~ y5
y3 ~~ y4
y3 ~~ y5
y4 ~~ y5
"

```
